GVN-Hoist: Hoisting Computations from Branches

### 2016-08-23 hoist.tex
more cleanups

\subsection{Code generation}
Once all the legality checks and profitability checks are satisfied for a set of
identical instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed. After that SSA form is restored by updating the
intermediate representation (IR) to reflect changes. After one iteration of
algorithm runs through the entire function, it creates more oppportunities for
\emph{higher ranked} computations \cite{rosen1988global}. Currently, we rerun
the algorithm until there are no more instructions left to be
hoisted. Obviously, this is not the most optimal approach and can be improved by
ranking the computations \cite{rosen1988global}.

\subsection{Verifying the post-conditions}
Performing a set of checks (e.g., consistency of use-defs and SSA semantics) to
establish that program invariants are maintained.

>>>>

\subsection{Code generation}
Once all the legality and profitability checks are satisfied for a set of
identical instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed, and the SSA form is restored by updating the
intermediate representation (IR) to reflect the changes.

After one iteration of algorithm runs through the entire function, it creates
more oppportunities for \emph{higher ranked} computations
\cite{rosen1988global}. Currently, this is a limitation of the GVN analysis
pass, and so we rerun the code-hoisting algorithm until there are no more
instructions left to be hoisted.  Obviously, this is not the most optimal
approach and can be improved by ranking the computations \cite{rosen1988global},
or by improving the GVN analysis to correctly number loads and dependent
instructions.

Finally after the transform is done, we verify a set of post-conditions to
establish that program invariants are maintained: e.g., consistency of
use-defs, and SSA semantics.
